### 2024-03-27 tesis_Ashish/Chapter5/chapter5.tex
update 27 Mar

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.3 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.4 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.6 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.5 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

>>>>

\begin{table}[H]
  \centering
  \caption[Systematic uncertainty in 2022 luminosity measurement]{Systematic uncertainty in 2022 luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.2 \\
        Ghost and satellite charges & 0.2 \\
        Orbit drift & 0.1 \\
        Residual beam positions & 0.3 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.6 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.2 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.4 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}
